% Tagged PDF setup — produces accessible PDF with structure tags.
\DocumentMetadata{
  lang = en,
  pdfstandard = a-2b,
  pdfstandard = ua-1,
  pdfversion = 2.0,
  testphase = {phase-II},
}
\documentclass[10pt]{article}

% {{{ packages
\usepackage{hyperref}
\usepackage{calc}
\usepackage[paper=letterpaper,
            marginparwidth=0.9in,     % Length of section titles
            marginparsep=.06in,       % Space between titles and text
            left=1.75in,
            right=-0.1in,
            top=0.7in,
            bottom=0.7in,
            includemp]{geometry}
\usepackage{etoolbox}
\usepackage{fontspec}
\usepackage[backend=biber,maxnames=99,style=numeric,sorting=ydnt,defernumbers]{biblatex} %sorting=ydnt
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{xcolor}
\setmainfont{TeX Gyre Pagella}
\setmonofont{Inconsolatazi4-Regular.otf}[BoldFont=Inconsolatazi4-Bold.otf]
\usepackage{fontawesome5}
\usepackage{paralist}
\usepackage{orcidlink}

\usepackage{luatexko}
\setmainfont{TeX Gyre Pagella}
\setmainhangulfont{Noto Serif CJK KR}
\setsanshangulfont{Noto Sans CJK KR}

% }}}

% bibliography  {{{
\addbibresource{byunghwee.bib}


% Highlight Me
% Highlight HAVI collaborators
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\newcommand*{\highlightname}[1]{\textcolor{darkblue}{\textbf{#1}}}

\newcommand*{\ishavicollaborator}{%
  \ifboolexpr{
    ( test {\ifdefstring{\namepartfamily}{Schich}} and test {\ifdefstring{\namepartgiven}{Maximilian}} )
    or
    ( test {\ifdefstring{\namepartfamily}{Ahn}} and test {\ifdefstring{\namepartgiven}{Yong-Yeol}} )
  }%
}

% Highlight me
\newcommand*{\isme}{%
  \ifboolexpr{
    test {\ifdefstring{\namepartfamily}{Lee}} and
    test {\ifdefstring{\namepartgiven}{Byunghwee}}
  }%
}

% Byunghwee name addon per entry
\newcommand*{\meaddon}{%
  \iffieldequalstr{entrykey}{kim2025investigating}{\textsuperscript{$\dagger$}}{}%
  \iffieldequalstr{entrykey}{kim2020multi}{\textsuperscript{$\dagger$}}{}%
  \iffieldequalstr{entrykey}{kim2025combined}{\textsuperscript{$\ast$}}{}%
}

\renewcommand*{\mkbibnamefamily}[1]{%
  \isme{{\bfseries\boldmath #1\meaddon}}{#1}%
}

\renewcommand*{\mkbibnamegiven}[1]{%
  \isme{{\bfseries\boldmath #1}}{#1}%
}

% Layouts  {{{
\reversemarginpar
\setlength{\parindent}{0in}

% page numbers
% page numbers
\pagestyle{fancy}
\fancyhf{}                       % header/footer 모두 초기화
\renewcommand{\headrulewidth}{0pt} % 위쪽 선 제거
\renewcommand{\footrulewidth}{0pt}

\fancyfootoffset{\marginparsep+\marginparwidth}


\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
                    \hfill \,}}
%}}}

%{{{ Fonts and colors
\linespread{1.05}        % Tighter than full CV

\definecolor{darkpink}{rgb}{0.48,0.13,0.13}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkpink,urlcolor=darkpink,
            anchorcolor=darkpink,citecolor=darkpink,
            pdftitle={Curriculum Vitae - Byunghwee Lee},
            pdfauthor={Byunghwee Lee},
            pdfsubject={Academic CV},
            pdflang={en},
            pdfdisplaydoctitle=true}
%}}}


%\newcommand{\makeheading}[2]{%
%{\hspace*{-\marginparsep minus \marginparwidth}%
%\begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
%{\Large \textbf{#1}} \, {\Large \textbf{#2}} \\
%\rule{\columnwidth}{.1pt} %
%\end{minipage}
%}
%}

\newcommand{\makeheading}[2]{%
{\hspace*{-\marginparsep minus \marginparwidth}%
\begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
{\Large \textbf{#1}} \, {\Large \textbf{#2}}%
\hfill {\normalsize Last updated: \today}\\
\rule{\columnwidth}{.1pt} %
\end{minipage}
}
}


%{{{ Sections
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{%
         \raggedright \scshape #1}#2}
\renewcommand{\subsection}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{subsection}{#1}%
         \hspace{0in} \textbf{#1} #2}




\newcommand{\blankline}{\quad\pagebreak[2]}
%}}}

%{{{ Lists
\newenvironment{outerlist}[1][\enskip\textbullet]%
{\vspace{-0.5\baselineskip}\begin{itemize}[#1]}{\setlength{\partopsep}{0pt}\setlength{\topsep}{0pt}\end{itemize}\vspace{-1\baselineskip}}

\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt} }}
        {\end{list}\vspace{-1\baselineskip}}

\newenvironment{innerlist}[1][\enskip\textbullet]%
{\vspace{0.2\baselineskip}\begin{compactitem}[#1]}{\end{compactitem}\vspace{0.2\baselineskip}}
%}}}

\begin{document}

%{{{ Name
\makeheading{Byunghwee}{Lee}
%}}}

\vspace{0.3\baselineskip}
\noindent
\textit{My research lies at the intersection of AI, data science, and society, where I develop computational methods to study art and culture, human beliefs, and social dynamics at scale.}


%{{{ Contact information
\section{Contact Information}{
\newlength{\rcollength}\setlength{\rcollength}{2.1in}%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength+20pt}p{\rcollength-20pt}}
Postdoctoral Research Associate & \faEnvelope~\href{mailto:wzn3hf@virginia.edu}{\texttt{wzn3hf@virginia.edu}}\\
School of Data Science, University of Virginia & \faOrcid~\href{https://orcid.org/0000-0003-2369-2022}{\texttt{0000-0003-2369-2022}}\\
1919 Ivy Rd., Charlottesville, VA 22903
\end{tabular}}
%}}}

\section{Research Interests}
Computational Social Science, Cultural Analytics, Computational Art History, Network Science, Representation Learning, Generative/Multimodal AI.


\section{Highlights}
\textbf{AI and Human Beliefs}
\begin{innerlist}
\item \textbf{Belief representation with LLMs}: 
\emph{Nature Human Behavior}, 2025; 
\emph{arXiv preprint}, 2025
\end{innerlist}

\textbf{Network Science, Social Systems, and Online Media}
\begin{innerlist}
\item \textbf{Network Dynamics of Social Media}: 
\emph{Physica A}, 2025; 
\emph{Phys. Rev. Res.}, 2021

\item \textbf{Online Discourse and Infodemics}: 
\emph{Explainable AI in Healthcare and Medicine}, 2020; 
\emph{Public Health and Informatics}, 2021; 
\emph{한국사회}, 2020
\end{innerlist}

\textbf{Data-driven Analysis of Art, Culture, and Creativity}
\begin{innerlist}
\item \textbf{Computational Art History}: 
\emph{PNAS}, 2020; 
\emph{Sci. Rep.}, 2025; 
\emph{PLOS One}, 2018; 
\emph{New Phys.: Sae Mulli}, 2016

\item \textbf{Multimodal AI for Art}: 
\emph{arXiv preprint}, 2025; 
\emph{SSRN preprint}, 2025

\item \textbf{Stylometry and Historical Texts}: 
\emph{JKPS}, 2020; 
\emph{New Phys.: Sae Mulli}, 2016
\end{innerlist}



\section{Selected Publications}
\textbf{Belief and AI} — \textbf{A semantic embedding space based on large language models for modelling human beliefs}.  
Byunghwee Lee, Rachith Aiyappa, Yong-Yeol Ahn, Haewoon Kwak, and Jisun An.  
\textit{Nature Human Behaviour}, 2025.  
\href{https://doi.org/10.1038/s41562-025-02228-z}{[Link]}

\begin{innerlist}
\item Highlighted by \textit{Phys.org}  
\href{https://phys.org/news/2025-06-llms-delve-online-debates-human.html}{[News]}
\end{innerlist}
\vspace{0.4\baselineskip}

\textbf{Art and Data Science} — \textbf{Dissecting landscape art history using information theory}.  
Byunghwee Lee, Min Kyung Seo, Daniel Kim, In-Seob Shin, Maximilian Schich, Hawoong Jeong, and Seung Kee Han.  
\textit{Proceedings of the National Academy of Sciences (PNAS)}, 117(43), 26580–26590 (2020).  
\href{https://doi.org/10.1073/pnas.2011927117}{[Link]}

\begin{innerlist}
\item Featured in the \textit{PNAS “In This Issue”} section  

\item Accompanied by a commentary paper  
\href{https://doi.org/10.1073/pnas.2018652117}{[Link]}

\item Highlighted by media including \href{https://www.forbes.com/sites/evaamsen/2020/10/23/math-shows-how-the-composition-of-landscape-paintings-changed-over-time/}{\textit{Forbes}}, \href{https://www.inverse.com/science/math-uncovers-art-secrets}{\textit{Inverse}}, \href{https://www.sciencedaily.com/releases/2020/11/201113105835.htm}{\textit{Science Daily}}, 
\href{https://kaist.ac.kr/news/html/news/?mode=V&mng_no=10630&skey=keyword&sval=%eb%b3%b5%ec%9e%a1%ea%b3%84&list_s_date=&list_e_date=&GotoPage=1}{KAIST News},
\href{https://www.dongascience.com/news/41209}{\textit{Donga Science}}, and
\href{https://dl.dongascience.com/dl/magazine/detail/S202103N016}{과학동아}. 
\end{innerlist}
\vspace{0.4\baselineskip}

\textbf{Network Science} — \textbf{Network analysis reveals news press landscape and asymmetric user polarization}.  
Byunghwee Lee, Hyo-sun Ryu, Jae Kook Lee, Hawoong Jeong, Beom Jun Kim. 
\textit{Physica A: Statistical Mechanics and its Applications}, p.130842 (2025)
\href{https://doi.org/10.1016/j.physa.2025.130842}{[Link]}
\begin{innerlist}
\item Highlighted by \textit{SKKU Media}  
\href{https://www.skku.edu/skku/campus/skk_comm/news.do?mode=view&articleNo=129197}{[News]}
\end{innerlist}

%}}}

%{{{ Education
\section{Education}
Ph.D. Physics, KAIST (Daejeon, South Korea) \hfill Feb. 2021
\begin{innerlist}
    \item[] Dissertation: \emph{Art and Complexity in the Era of Big Data} (Advisor: Hawoong Jeong)
\end{innerlist}
B.S. Physics, KAIST (Daejeon, South Korea)\hfill Feb. 2013



%{{{ Positions
\section{Academic \& Professional Positions}
\textbf{University of Virginia}, Charlottesville, VA, USA
\begin{innerlist}
\item[] Postdoctoral Research Associate (Advisor: Yong-Yeol Ahn) \hfill Aug. 2025--
\end{innerlist}
\textbf{Indiana University}, Bloomington, IN, USA
\begin{innerlist}
\item[] Postdoctoral Researcher, Luddy School of Informatics, Computing, and Engineering
\\ (Advisor: Jisun An, Haewoon Kwak, and Yong-Yeol Ahn) \hfill Mar. 2023 -- Aug. 2025
\end{innerlist}
\textbf{Sungkyunkwan University}, South Korea
\begin{innerlist}
\item[] Senior researcher, Institute of Basic Science (Advisor: Beom Jun Kim) \hfill Sep. 2022 -- Feb. 2023
\end{innerlist}
\textbf{National Science Museum}, South Korea
\begin{innerlist}
\item[] Researcher / Curator \hfill Jun. 2021 -- Sep. 2022
\item[] Contributed to the advancement of museum data management system
\end{innerlist}
\textbf{Korea Advanced Institute of Science and Technology (KAIST)}, South Korea
\begin{innerlist}
\item[] Post-doctoral researcher, Natural Science Research Institute\\ (Advisor: Hawoong Jeong) \hfill Mar. 2021 -- Jun. 2021
\end{innerlist}



\section{Professional License}
{\textbf{National Certificate on Museum and Art Gallery Curator (level 3)}
\begin{innerlist}
\item[] Ministry of Culture, Sports and Tourism, South Korea \hfill Oct. 2022
\end{innerlist}}

\section{Awards}
\textbf{Oral and Poster Presentation Awards}
\begin{innerlist}
\item[] Datapalooza 2025 Best in Show Award, School of Data Science, University of Virginia\\(\textit{\$750 Travel award})
\href{https://datascience.virginia.edu/news/postdoctoral-researcher-byunghwee-lee-wins-best-show-datapalooza-2025}{[News]}
\hfill Nov.~2025

\item[] Korean Physical Society Meeting, Best Poster Presentation
\hfill Jul.~2020

\item[] Korean Physical Society Meeting, Best Oral Presentation
\hfill Apr.~2019

\item[] Korea Academy of Complexity Studies,\\ Best Oral Presentation \hfill Nov. 2013; Nov. 2014; Nov. 2015; Nov. 2017

\item[] Conference on Complex Systems (Arizona, USA), Best Poster Award 
\hfill Oct.~2015

\item[] STATPHYS25 Satellite Meeting: Computational Methods for Bio and Complex Systems \\Best Poster Award
\hfill Jul.~2013
\end{innerlist}






\section{Selected Media Coverage}
\textbf{Selected media coverage of research}
\begin{innerlist}
\item LLMs delve into online debates to create a detailed map of human beliefs, \textit{Phys.org}, Jun. 2025. \href{https://phys.org/news/2025-06-llms-delve-online-debates-human.html}{[News]}

\item The human quest for discovering mathematical beauty in the arts, \emph{PNAS} Commentary, October 23, 2020. \href{https://www.pnas.org/doi/10.1073/pnas.2018652117}{[Link]}

\item Math shows How the composition of landscape paintings changed over time, \textit{Forbes}, Oct. 23. 2020. \href{https://www.forbes.com/sites/evaamsen/2020/10/23/math-shows-how-the-composition-of-landscape-paintings-changed-over-time/}{[Link]} 

\item Math uncovers hidden patterns in these historic art masterpieces, \textit{Inverse}, Oct. 13. 2020. \href{https://www.inverse.com/science/math-uncovers-art-secrets}{[Link]}

\item Drawing the Line to Answer Art’s Big Questions, \textit{KAIST News} \href{https://kaist.ac.kr/news/html/news/?mode=V&mng_no=10630&skey=keyword&sval=%eb%b3%b5%ec%9e%a1%ea%b3%84&list_s_date=&list_e_date=&GotoPage=1}{[Link]}

\item 명화 속 빛의 비밀, 데이터는 알고 있다 (\textit{Data reveals the hidden secrets of light in masterpieces}), \textit{과학동아}, Mar. 2021. \href{https://dl.dongascience.com/dl/magazine/detail/S202103N016}{[Link]} 

\item 학제 간 경계를 넘은 융합 연구, 양극화된 댓글 네트워크를 확인하다 (\textit{Interdisciplinary research across boundaries reveals polarized comment networks}), \textit{SKKU Media}, Aug. 2025.
\href{https://www.skku.edu/skku/campus/skk_comm/news.do?mode=view&articleNo=129197}{[Link]}
\end{innerlist}


%\section{Publications}
%\textbf{Peer-reviewed Publications\\($^\dagger$: equal contribution; $^\ast$: Co-corresponding author)}
%{\renewcommand*{\bibfont}{}\printbibliography[heading=none]}


\section{Publications}
\textbf{Preprints and Manuscripts Under Review\\($^\dagger$: equal contribution; $^\ast$: Co-corresponding author)}
\begin{refsection}
\nocite{*}
{\DeclareFieldFormat{labelnumberwidth}{\mkbibbrackets{P#1}}%
 \renewcommand*{\bibfont}{}%
 \printbibliography[
   heading=none,
   keyword=preprint,
   resetnumbers=true
 ]}
\end{refsection}

\textbf{Peer-reviewed Publications\\($^\dagger$: equal contribution; $^\ast$: Co-corresponding author)}
\begin{refsection}
\nocite{*}
{\renewcommand*{\bibfont}{}\printbibliography[
  heading=none,
  keyword=peerreviewed,
  resetnumbers=true
]}
\end{refsection}

%In preparation
\textbf{Manuscripts in Preparation}
\begin{innerlist}
\item \textbf{The geometry of persuasion: Quantifying belief change in a latent embedding space}.  
\textbf{Byunghwee Lee}, Jisun An, Haewoon Kwak, Yong-Yeol Ahn.  
\emph{In preparation}.

\end{innerlist}

\section{Articles and Book chapters}
\textbf{Articles and Magazines}
\begin{innerlist}

\item \textbf{Math reveals the evolution of composition in paintings}, 
Byunghwee Lee, Hawoong Jeong, 
\textit{The Science Breaker}, Dec. 29. 2021. 
\href{https://doi.org/10.25250/thescbr.brk609}{[Link]}

\item \textbf{Art history seen through the eyes of physics (in Korean)}, 
Byunghwee Lee, 
\textit{APCTP Crossroad Webzine}, Apr. 2021. 
\href{https://webzine.kps.or.kr/?p=5_view&idx=16551}{[Link]}

\item \textbf{네트워크 과학으로 살펴보는 사회적 거리두기와 접촉자 추적의 원리 
(Principles of Social Distancing and Contact Tracing through Network Science)}, 
Byunghwee Lee, Hawoong Jeong, 
\textit{BT News} (Newsletter of the Korean Society of Biotechnology), Apr. 2021. 
\href{https://www.dbpia.co.kr/Journal/articleDetail?nodeId=NODE10553023}{[Link]}
\end{innerlist}

\textbf{Book Chapters}
\begin{innerlist}
\item \textbf{전염의 복잡계 과학적 접근 
(Complex Science Approaches to the Contagion Phenomena)}, 
Byunghwee Lee, Hawoong Jeong, 
in \textit{Imagination of Contagion}, pp.~101--137, 2017.
\end{innerlist}


\section{Teaching Experience}
\textit{Courses assisted:} Nonlinear Dynamics, Thermal Physics, College Physics, General Physics.

\begin{innerlist}

\item \textbf{Instructor} Python-Based Big Data Analysis Workshop,  
Department of Sociology, Korea University \hfill May--June 2020\\  
- Designed and taught a six-session workshop on Python-based data analysis covering Python fundamentals, text analysis, topic modeling, and network analysis through lectures and hands-on labs.

\item \textbf{Undergraduate Research Mentor} \hfill 2020--2021 \\
- Supervised Sang Jin Jeon on \textit{information-spectrum-based analysis of musical structure}.

\item \textbf{Independent Research Mentor}  
Institut Teknologi Bandung (ITB) -- KAIST Undergraduate Exchange Program \hfill Oct.--Nov. 2015 \\ 
- Mentored Ridho Muhammad Akbar on \textit{network-based spatial analysis of climate change data}.

\item \textbf{Teaching Assistant}, Department of Physics, KAIST  \\ 
- Nonlinear Dynamics \hfill Fall 2015  \\
- Thermal Physics (led recitation sections) \hfill Spring 2015  \\
- College Physics (led recitation sections) \hfill Spring 2014  \\
- General Physics (led recitation sections) \hfill Spring 2013  
\end{innerlist}

\section{Peer Review Service}
Reviewer for: 
\textit{EPJ Data Science}, 
\textit{Scientific Reports}, 
\textit{ICWSM}, 
\textit{PLOS ONE}, 
\textit{The Web Conference PhD Symposium}, 
\textit{Advances in Complex Systems}, 
\textit{Humanities and Social Sciences Communications}, 
\textit{New Physics: Sae Mulli}.

\section{Skills}
\textbf{Programming and Data Science:}
Python (NumPy, Pandas, SciPy), PyTorch, Scikit-Learn, NetworkX, parallel computing, machine learning, natural language processing, large language model APIs (OpenAI, Hugging Face).

\textbf{Data Analysis and Visualization:}
Network analysis, text analysis, topic modeling, data visualization (Matplotlib, d3.js), network visualization tools (Gephi).

\textbf{Software and Tools:}
Git, Linux/Unix, LaTeX, Adobe Illustrator, Final Cut Pro.

\textbf{Other Programming Languages:}
Matlab, R, Java, HTML/CSS, Processing.

\textbf{Languages:}
Korean (Native), English (Professional proficiency).


\section{Conference Presentations}
\textbf{2026}
\begin{innerlist}
\item (Poster) \textbf{Byunghwee Lee}, Haewoon Kwak, Jisun An, Yong-Yeol Ahn\\
\textit{Social judgement theory in a belief embedding space} NetSci 2026, Boston, MA, USA, June 1-5, 2026.
\end{innerlist}


\textbf{2025}
\begin{innerlist}
\item (Oral) \textbf{Byunghwee Lee}, Sangyeon Kim, Filippo Menczer, Yong-Yeol Ahn, Haewoon Kwak, Jisun An.\\
\textit{Can LLMs infer political affiliation from non-political discourse?} International Conference on Computational Social Science (IC2S2), Norrköping, Sweden, Jul. 2025.
\end{innerlist}

\textbf{2024}
\begin{innerlist}
\item (Plenary talk) \textbf{Byunghwee Lee}, Rachith Aiyappa, Yong-Yeol Ahn, Haewoon Kwak, Jisun An.\\
\textit{Neural embedding of beliefs reveals the role of relative dissonance in human decision-making}. International Conference on Computational Social Science (IC2S2), Philadelphia, USA, Jul. 2024.

\item (Poster) Taekho You (presenter), Jin Kim, \textbf{Byunghwee Lee}, Jinhyuk Yun.\\
\textit{Understanding the Creativity through Evolution of Western Painting Art Using the Stable Diffusion Model}. International Conference on Computational Social Science (IC2S2), Philadelphia, USA, Jul. 2024.
\end{innerlist}

\textbf{2020}
\begin{innerlist}
\item (Poster) \textbf{Byunghwee Lee}, Min Kyung Seo, Daniel Kim, In-seob Shin, Maximilian Schich, Hawoong Jeong, Seung Kee Han.\\
\textit{Information-theoretic dissection of painting reveals the evolution of composition of landscape painting}. NetSci, Rome (Virtual), Sep. 2020.

\item (Poster) \textbf{Byunghwee Lee}, Min Kyung Seo, Daniel Kim, In-seob Shin, Maximilian Schich, Hawoong Jeong, Seung Kee Han.\\
\textit{Revealing the evolution of composition of landscape painting through the lens of information theory}. Korean Physical Society Meeting (Virtual), Jul. 2020.
\end{innerlist}

\textbf{2019}
\begin{innerlist}
\item (Oral) \textbf{Byunghwee Lee}, Daniel Kim, Dongwoo Kim, Hawoong Jeong.\\
\textit{Information-theoretic dissection of landscape paintings reveals conceptual overlap in art historiography}. Statistical Physics Workshop, Oct. 2019.

\item (Poster) \textbf{Byunghwee Lee}, Min Kyung Seo, Daniel Kim, In-seob Shin, Hawoong Jeong, Seung Kee Han.\\
\textit{Information-theoretic analysis of composition in painting and the composition-similarity network of painters}. NetSci, University of Vermont, May 2019.

\item (Oral) \textbf{Byunghwee Lee}, Daniel Kim, Dongwoo Kim, Hawoong Jeong.\\
\textit{Large-scale information theoretic analysis of composition in painting}. Korean Physical Society Meeting, Apr. 2019.
\end{innerlist}

\textbf{2017}
\begin{innerlist}
\item (Oral) \textbf{Byunghwee Lee}, Daniel Kim, Hawoong Jeong.\\
\textit{Inferring Posthumous Fame from Social Network Location Using a Half Millennium Historical Documents}. Korean Society of Complex Systems Conference, 2017.

\item (Oral) \textbf{Byunghwee Lee}, Daniel Kim, Hawoong Jeong.\\
\textit{Historical records and patterns of fame}. KAIST Econophysics Workshop, 2017.

\item (Oral) \textbf{Byunghwee Lee}, Daniel Kim, Hawoong Jeong.\\
\textit{Inferring Posthumous Fame from Social Network Location Using a Half Millennium Historical Documents}. Statistical Physics Workshop, 2017.
\end{innerlist}

\textbf{2016}
\begin{innerlist}
\item (Oral) \textbf{Byunghwee Lee}, Daniel Kim, Hawoong Jeong.\\
\textit{Analysis of Spatio-temporal Pattern of Historical Cities in the Annals of the Joseon Dynasty}. Workshop on Special Topics in Statistical Physics \& Complex Systems, 2016.

\item (Oral) \textbf{Byunghwee Lee}, Kibum Kim, Daniel Kim, Beom Jun Kim, Hawoong Jeong.\\
\textit{Understanding spatiotemporal patterns in the Annals of the Joseon Dynasty}. Korean Physical Society Fall Meeting, 2016.

\item (Oral) \textbf{Byunghwee Lee}, Daniel Kim, Hawoong Jeong, Seunghye Sun, Juyong Park.\\
\textit{Quantitative analysis on contrast effect in the evolution of paintings}. STATPHYS 26, 2016.

\item (Oral) \textbf{Byunghwee Lee}, Daniel Kim, Hawoong Jeong, Seunghye Sun, Juyong Park.\\
\textit{Quantitative analysis of color contrast in the evolution of painting}. NetSci, 2016.
\end{innerlist}

\textbf{2015}
\begin{innerlist}
\item (Oral) \textbf{Byunghwee Lee}, Daniel Kim, Hawoong Jeong, Juyong Park.\\
\textit{Evolution of color contrast in art history}. Korean Society of Complex Systems Conference, 2015.

\item (Oral) \textbf{Byunghwee Lee}, Daniel Kim, Hang-Hyun Jo, Hawoong Jeong.\\
\textit{Quantitative analysis of Joseon history using chronological data}. Korean Physical Society Meeting, 2015.

\item (Poster) \textbf{Byunghwee Lee}, Daniel Kim, Hang-Hyun Jo, Hawoong Jeong.\\
\textit{Understanding motives of historical events through the Annals of the Joseon Dynasty}. Conference on Complex Systems, 2015.
\end{innerlist}

\textbf{2014}
\begin{innerlist}
\item (Oral) \textbf{Byunghwee Lee}, Daniel Kim, Kihong Chung, Hawoong Jeong.\\
\textit{Network structure in the Annals of the Joseon Dynasty}. Korean Society of Complex Systems Conference, 2014.

\item (Poster) \textbf{Byunghwee Lee}, Daniel Kim, Kihong Chung, Hawoong Jeong.\\
\textit{Stylometry and Network Analysis on the Annals of the Joseon Dynasty}. Korean Physical Society Meeting, 2014.
\end{innerlist}

\textbf{2013}
\begin{innerlist}
\item (Oral) \textbf{Byung-hwee Lee}, Daniel Kim, Hawoong Jeong.\\
\textit{Statistical analysis of the Annals of the Joseon Dynasty}. Complex Systems Conference, 2013.

\item (Poster) \textbf{Byung-hwee Lee}, Daniel Kim, Hawoong Jeong.\\
\textit{Web Search Trend Based Social Network Construction}. Korean Physical Society Meeting, 2013.

\item (Poster) Daniel Kim, \textbf{Byung-hwee Lee}, Hawoong Jeong.\\
\textit{Quantitative Analysis of the Annals of the Joseon Dynasty}. STATPHYS 25, 2013.
\end{innerlist}


\section{Selected Invited Talks and Seminars}
\textbf{2025}
\begin{innerlist}
\item \textbf{A Semantic Embedding Space Based on Large Language Models for Modeling Human Beliefs}.\\
Max Planck Institute for Security and Privacy (MPI-SP) DSLAB Seminar, Aug. 2025.
\item \textbf{A Semantic Embedding Space Based on Large Language Models for Modeling Human Beliefs}.\\
KDI School, Jun. 2025.
\item \textbf{A Semantic Embedding Space Based on Large Language Models for Modeling Human Beliefs}.\\
Soongsil University, Jun. 2025.
\end{innerlist}

\textbf{2024}
\begin{innerlist}
\item \textbf{Network Analysis Reveals News Press Landscape and User Polarization}.\\
Sungkyunkwan University, Feb. 2024.
\end{innerlist}

\textbf{2023}
\begin{innerlist}
\item \textbf{Understanding Art and Culture through Data Science}.\\
Chonnam National University, Dec. 2023.
\end{innerlist}

\textbf{2022}
\begin{innerlist}
\item \textbf{Art and Artists through the Lens of Statistical Physics}.\\
Chosun University, Dec. 2022.
\item \textbf{Understanding Art and Culture through Data Science}.\\
Chonnam National University, Dec. 2022.
\end{innerlist}

\textbf{2021}
\begin{innerlist}

\item \textbf{Can We Understand Art through Physics? Art through the Lens of Complex Systems and Big Data}.\\
Chosun University, Oct. 2021.

\end{innerlist}





\end{document}

